\chapter{Experimental Setup}

To evaluate the mathematical correctness and hardware scalability of the ZKLR framework, we deployed the platform across both consumer-grade and enterprise-grade environments.

\section{Hardware and Environments}
The baseline Phase 1 experiments were conducted on an Apple Silicon M-series laptop featuring an 8-core CPU and 16 GB of unified memory. This environment provided the baseline single-thread compilation limits and general prove validation metrics.

For Phase 2 scaling tests, the workloads were offloaded to the High-Performance Computing (HPC) cluster at IIIT. The HPC nodes allocated up to 96 concurrent CPU cores, allowing us to evaluate the scaling thresholds of the parallelized worker-pool implementation against memory bottlenecks.

\input{tables/table_03_exp_setup.tex}

\section{Cryptographic and Software Stack}
The framework was built entirely in Go (v1.22), which natively supports lightweight threading via Goroutines. 

The underlying zero-knowledge components rely on \texttt{gnark} v0.11.0, executing the PLONK proving scheme over the \texttt{ecc.BN254} elliptic curve. We deliberately selected BN254 because of its widespread adoption and native support within the Ethereum Virtual Machine (EVM) via the \texttt{ecpairing} precompile contract. This ensures that the proofs generated in this experiment are fully compatible with current leading smart contract platforms.

\section{Datasets and Configurations}
Two synthetic datasets were synthesized to benchmark the pipeline under varying constraints:
\begin{enumerate}
    \item \textbf{Baseline Geometry:} A 2-feature dataset consisting of 100 samples mapped against a trained Body Mass Index (BMI) model. This served as the testing ground for the Phase 1 circuit.
    \item \textbf{Stress Test Geometry:} A scaled 4-feature dataset comprising 10,000 synthetically generated continuous features, separated into a 70\% training phase and a 30\% test phase (yielding 3,000 pure prediction validation targets). The underlying model achieved 70.67\% accuracy over binary classification tasks.
\end{enumerate}

To thoroughly evaluate the Phase 2 worker-pool layout across the 3,000 sample dataset, multiple matrix configurations were assessed. Variables tested included \textbf{Batch Size} (from groups of 20 up to 40 samples) and \textbf{Worker Granularity} (from 4 workers locally, up to 96 cores sequentially distributed on the HPC nodes).
