\chapter{Applications}

The ability to generate cryptographic evidence of machine learning model predictions opens up a vast space for trustless, high-stakes enterprise applications.

\section{Decentralized Autonomous Machine Learning Marketplaces}
In emerging Web3 ecosystems, data scientists can train expensive models (e.g., scoring credit worthiness) and host them off-chain. By employing the ZKLR framework, sellers can issue predictions down to users. Because consumers mathematically verify the PLONK proofs against the published Verification Key, they do freely exchange micro-transaction payments knowing definitively that the prediction wasn't forged or derived from an inferior/cheaper model architecture.

\section{Healthcare and HIPAA Regulations}
Healthcare institutions are legally forbidden from uploading unencrypted patient data (e.g., blood cell biomarkers in CSV structure) to cloud entities for analysis. Utilizing Zero-Knowledge platforms, hospitals could securely transmit encrypted variables; the cloud provider evaluates the proprietary diagnostic ML model alongside the ZKP, guaranteeing that the hospital accurately receives life-or-death diagnostics while protecting intellectual patient privacy.

\section{Compliance \& Auditing}
Financial algorithms used for mortgage loan approvals require regular audits to ensure algorithmic models aren't quietly biased against geographical minority sectors based on dynamic data fields. ZKLR enables a regulatory bureau to pass continuous dummy applicant profiles through the proprietary banking model, verifying via the proofs that the true, audited parameters were invoked, holding corporations mathematically accountable without compromising their trade-secret weight vectors.
